Risk Perceptions for Wearable Devices

### 2015-03-04 tex-inputs/long-tables/collapsed.tex
fixed long tables

\documentclass[a4paper,12pt]{article}
\usepackage[cm]{fullpage}
\usepackage{longtable}
\usepackage{graphicx}
\begin{document}
\begin{longtable}{| p{0.5cm} | p{7cm} | p{1cm} | c |}

\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} &  \multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
\endfirsthead

\multicolumn{3}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} &  \multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
\endhead

@@

1 & Tookavideoofyouunclothed & 95.97 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookavideoofyouunclothedcombined} \\ 
2 & Learnedyourbankaccountinformation & 95.91 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourbankaccountinformationcombined} \\ 
3 & Learnedyoursocialsecuritynumber & 94.84 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyoursocialsecuritynumbercombined} \\ 
4 & Tookavideoofyouenteringinyourpinatanatm & 92.67 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookavideoofyouenteringinyourPINatanATMcombined} \\ 
5 & Tookaphotoofyouunclothed & 92.59 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookaphotoofyouunclothedcombined} \\ 
6 & Tookanincriminatingphotoofyoudoingsomethingembarrassing & 91.39 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookanincriminatingphotoofyoudoingsomethingembarrassingcombined} \\ 
7 & Learnedyourusernameandpasswordforwebsites & 89.55 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourusernameandpasswordforwebsitescombined} \\ 
8 & Learnedyourcreditcardinformation & 88.98 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourcreditcardinformationcombined} \\ 
9 & Tookanincriminatingvideoofyoudoingsomethingembarrassing & 88.41 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookanincriminatingvideoofyoudoingsomethingembarrassingcombined} \\ 
10 & Tookphotosofyou(Withaninward-Facingcamera)Athome & 87.5 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookphotosofyou(withaninward-facingcamera)athomecombined} \\ 
11 & Recordedyourworkconversations & 86.82 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesrecordedyourworkconversationscombined} \\ 
12 & Tookavideoofyouenteringinadigitalpasscodetoalockeddoor & 85.53 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookavideoofyouenteringinadigitalpasscodetoalockeddoorcombined} \\ 
13 & Recordedyourphoneconversations & 85.16 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesrecordedyourphoneconversationscombined} \\ 
14 & Learnedhowmuchmoneyyouhave & 84.44 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedhowmuchmoneyyouhavecombined} \\ 
15 & Tookavideoofyouintoxicated & 83.21 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookavideoofyouintoxicatedcombined} \\ 
16 & Learnedwhenandhowmuchyouhavesex & 81.95 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenandhowmuchyouhavesexcombined} \\ 
17 & Tookvideosofyou(Withaninward-Facingcamera)Athome & 81.05 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookvideosofyou(withaninward-facingcamera)athomecombined} \\ 
18 & Tookaphotoofyouintoxicated & 78.95 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookaphotoofyouintoxicatedcombined} \\ 
19 & Tookphotosofyou(Withaninward-Facingcamera)Atrandom & 78.76 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookphotosofyou(withaninward-facingcamera)atrandomcombined} \\ 
20 & Recordedyourpassingconversations & 78.13 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesrecordedyourpassingconversationscombined} \\ 
21 & Learnedwhatmedicalconditionsyouhave & 77.7 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhatmedicalconditionsyouhavecombined} \\ 
22 & Tookvideosofyou(Withaninward-Facingcamera)Atrandom & 76.19 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookvideosofyou(withaninward-facingcamera)atrandomcombined} \\ 
23 & Tookavideoofyouoff-Guard & 76.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookavideoofyouoff-guardcombined} \\ 
24 & Tookphotosatwork(Withanoutward-Facingcamera) & 74.62 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookphotosatwork(withanoutward-facingcamera)combined} \\ 
25 & Learnedyourusernameforwebsites & 73.44 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourusernameforwebsitescombined} \\ 
26 & Learnedyouraddress & 72.61 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyouraddresscombined} \\ 
27 & Copiedanduploadedaudiorecordingsyoumadeonyourdevice & 72.55 & \includegraphics[width = 2cm, height = 0.5cm]{../tablescopiedanduploadedaudiorecordingsyoumadeonyourdevicecombined} \\ 
28 & Copiedanduploadedaudiorecordingsyoumadeonyourdevice & 72.55 & \includegraphics[width = 2cm, height = 0.5cm]{../tablescopiedanduploadedaudiorecordingsyoumadeonyourdevicecombined} \\ 
29 & Sharedphotosyoudownloadedfromtheinternetsavedonyourdevice & 71.81 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessharedphotosyoudownloadedfromtheinternetsavedonyourdevicecombined} \\ 
30 & Sharedphotosotherssenttoyousavedonyourdevice & 71.63 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessharedphotosotherssenttoyousavedonyourdevicecombined} \\ 
31 & Sharedvideosotherssentyousavedonyourdevice & 70.59 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessharedvideosotherssentyousavedonyourdevicecombined} \\ 
32 & Tookvideosatwork(Withanoutward-Facingcamera) & 70.54 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookvideosatwork(withanoutward-facingcamera)combined} \\ 
33 & Learnedyourfingerprintsomehow & 70.12 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourfingerprintsomehowcombined} \\ 
34 & Learnedwhenyouwerelyingnervousorstressed & 69.74 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenyouwerelyingnervousorstressedcombined} \\ 
35 & Recordedyoutalkingtoyourself(Makingvoicenotes) & 69.59 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesrecordedyoutalkingtoyourself(makingvoicenotes)combined} \\ 
36 & Learnedwhatmedicationyoutake & 69.49 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhatmedicationyoutakecombined} \\ 
37 & Sharedvideosyoutookwhicharealreadyonyourdevice & 68.89 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessharedvideosyoutookwhicharealreadyonyourdevicecombined} \\ 
38 & Tookapictureofyoursignature & 68.07 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookapictureofyoursignaturecombined} \\ 
39 & Learnedwhatwebsitesyougoto & 66.44 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhatwebsitesyougotocombined} \\ 
40 & Sharedphotosyoutookwhicharealreadyonyourdevice & 66.21 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessharedphotosyoutookwhicharealreadyonyourdevicecombined} \\ 
41 & Learnedwhereyoulivesomehow & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhereyoulivesomehowcombined} \\ 
42 & Trackedwhereyouareveryaccurately(Whereyouareinaroom) & 63.51 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestrackedwhereyouareveryaccurately(whereyouareinaroom)combined} \\ 
43 & Tookphotosofpeople(Withanoutward-Facingcamera)Atrandom & 61.94 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookphotosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
44 & Sharedvideosyoudownloadedontheinternetsavedonyourdevice & 61.49 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessharedvideosyoudownloadedontheinternetsavedonyourdevicecombined} \\ 
45 & Learnedwhenandhowmuchyouspendtimealone & 61.27 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenandhowmuchyouspendtimealonecombined} \\ 
46 & Trackedwhereyouare(Likeagps) & 61.24 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestrackedwhereyouare(likeaGPS)combined} \\ 
47 & Tookvideosofpeople(Withanoutward-Facingcamera)Atrandom & 61.04 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookvideosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
48 & Learnedwhereyouarecurrentlygoing & 60.87 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhereyouarecurrentlygoingcombined} \\ 
49 & Recordedthesoundaroundyou & 60.45 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesrecordedthesoundaroundyoucombined} \\ 
50 & Learnedwhoyouwerespendingtimewith & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhoyouwerespendingtimewithcombined} \\ 
51 & Learnedwhereyouworksomehow & 58.09 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhereyouworksomehowcombined} \\ 
52 & Copiedanduploadedsoundssavedonyourdevice(Notificationnoisesetc) & 54.4 & \includegraphics[width = 2cm, height = 0.5cm]{../tablescopiedanduploadedsoundssavedonyourdevice(notificationnoisesetc)combined} \\ 
53 & Learnedhowmuchyouuseyourphone & 51.95 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedhowmuchyouuseyourphonecombined} \\ 
54 & Learnedwhatproductsyoubuy & 50.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhatproductsyoubuycombined} \\ 
55 & Learnedwhenyouaresickorhealthy & 48.17 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenyouaresickorhealthycombined} \\ 
56 & Learnedhowcloseyouaretootherpeopleyouinteractwith & 46.98 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedhowcloseyouaretootherpeopleyouinteractwithcombined} \\ 
57 & Learnedhowyouwerefeelingbasedonheartratebreathingandortemperature & 46.81 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedhowyouwerefeelingbasedonheartratebreathingandortemperaturecombined} \\ 
58 & Learnedhowmuchyouuseyourcomputer & 44.93 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedhowmuchyouuseyourcomputercombined} \\ 
59 & Learnedwhenhowmuchandwhatyouareeating & 42.86 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenhowmuchandwhatyouareeatingcombined} \\ 
60 & Learnedyourname & 42.54 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyournamecombined} \\ 
61 & Learnedwhenandhowwellyouaresleeping & 40.56 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenandhowwellyouaresleepingcombined} \\ 
62 & Scannedyoureyetolearnyoureyepatterns(Foreyetracking) & 40.51 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesscannedyoureyetolearnyoureyepatterns(foreyetracking)combined} \\ 
63 & Learnedwhenhowandhowmuchyouexercise & 38.66 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenhowandhowmuchyouexercisecombined} \\ 
64 & Learnedwhenyouwerehappyorhavingfun & 34.75 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenyouwerehappyorhavingfuncombined} \\ 
65 & Learnedwhattelevisionshowsyouwatch & 30.2 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhattelevisionshowsyouwatchcombined} \\ 
66 & Learnedwhenyouarebusyorinterruptible & 29.5 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenyouarebusyorinterruptiblecombined} \\ 
67 & Copiedanduploadedmusicfromyourdevice & 28.06 & \includegraphics[width = 2cm, height = 0.5cm]{../tablescopiedanduploadedmusicfromyourdevicecombined} \\ 
68 & Learnedyourheartrate & 27.5 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourheartratecombined} \\ 
69 & Learnedyourage & 24.29 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyouragecombined} \\ 
70 & Learnedthelanguageyouwerespeaking & 15.86 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedthelanguageyouwerespeakingcombined} \\ 
71 & Learnedyourgender & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourgendercombined} \\ 

>>>>

\documentclass[a4paper,12pt]{article}
\usepackage[cm]{fullpage}
\usepackage{longtable}
\usepackage{graphicx}
\begin{document}
\begin{longtable}{| p{0.5cm} | p{7cm} | p{1cm} |p{1cm} | c |}

\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} &  \multicolumn{1}{c|}{\textbf{Standard Deviation}} &\multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
\endfirsthead

\multicolumn{3}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} & \multicolumn{1}{c|}{\textbf{Standard Deviation}} & \multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
\endhead

@@

1 & video of you unclothed & 95.97 & 0.31 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookavideoofyouunclothedcombined} \\ 
2 & bank account information & 95.91 & 0.35 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedyourbankaccountinformationcombined} \\ 
3 & social security number & 94.84 & 0.26 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedyoursocialsecuritynumbercombined} \\ 
4 & video entering in a PIN at an ATM & 92.67 & 0.48 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookavideoofyouenteringinyourPINatanATMcombined} \\ 
5 & photo of you unclothed & 92.59 & 0.45 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookaphotoofyouunclothedcombined} \\ 
6 & photo of you that is very embarrassing & 91.39 & 0.56 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookanincriminatingphotoofyoudoingsomethingembarrassingcombined} \\ 
7 & username and password for websites & 89.55 & 0.62 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedyourusernameandpasswordforwebsitescombined} \\ 
8 & credit card information & 88.98 & 0.56 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedyourcreditcardinformationcombined} \\ 
9 & video of you that is very embarrassing & 88.41 & 0.53 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookanincriminatingvideoofyoudoingsomethingembarrassingcombined} \\ 
10 & photo of you at home & 87.5 &0.60 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookphotosofyou(withaninward-facingcamera)athomecombined} \\ 
11 & audio recording of work conversations & 86.82 & 0.76 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/recordedyourworkconversationscombined} \\ 
12 & video of entering in a passcode to a door & 85.53 & 0.62 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookavideoofyouenteringinadigitalpasscodetoalockeddoorcombined} \\ 
13 & audio recording of phone conversations & 85.16 & 0.61 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/recordedyourphoneconversationscombined} \\ 
14 & amount of money you have & 84.44 & 0.61 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedhowmuchmoneyyouhavecombined} \\ 
15 & video of you intoxicated & 83.21 & 0.72 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookavideoofyouintoxicatedcombined} \\ 
16 & when you have sex & 81.95 & 0.82 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhenandhowmuchyouhavesexcombined} \\ 
17 & video of you at home & 81.05 & 0.60 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookvideosofyou(withaninward-facingcamera)athomecombined} \\ 
18 & photo of you intoxicated & 78.95 & 0.82 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookaphotoofyouintoxicatedcombined} \\ 
19 & photo of you at random & 78.76 & 0.85 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookphotosofyou(withaninward-facingcamera)atrandomcombined} \\ 
20 & audio recording of conversations & 78.13 & 0.83 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/recordedyourpassingconversationscombined} \\ 
21 & medical conditions & 77.7 & 0.86 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhatmedicalconditionsyouhavecombined} \\ 
22 & video of you at random & 76.19 & 0.59 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookvideosofyou(withaninward-facingcamera)atrandomcombined} \\ 
23 & video of you off-guard & 76.0 & 0.62 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookavideoofyouoff-guardcombined} \\ 
24 & photo of your work or workplace & 74.62 & 0.90 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookphotosatwork(withanoutward-facingcamera)combined} \\ 
25 & username for websites & 73.44 & 0.83 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedyourusernameforwebsitescombined} \\ 
26 & address & 72.61 & 0.86 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedyouraddresscombined} \\ 
27 & audio recording you captured & 72.55  & 0.70 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/copiedanduploadedaudiorecordingsyoumadeonyourdevicecombined} \\ 
28 & photo of you off-guard & 72.55 & 0.77 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookaphotoofyouoff-guardcombined} \\ 
29 & photo downloaded from internet & 71.81 & 0.90 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/sharedphotosyoudownloadedfromtheinternetsavedonyourdevicecombined} \\ 
30 & photo others sent you & 71.63 & 1.03 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/sharedphotosotherssenttoyousavedonyourdevicecombined} \\ 
31 & video others sent you & 70.59 & 0.81 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/sharedvideosotherssentyousavedonyourdevicecombined} \\ 
32 & video of your work or workplace & 70.54 & 0.90 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookvideosatwork(withanoutward-facingcamera)combined} \\ 
33 & fingerprint & 70.12 & 0.86 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedyourfingerprintsomehowcombined} \\ 
34 & when you were lying nervous or stressed & 69.74 & 0.91 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhenyouwerelyingnervousorstressedcombined} \\ 
35 & audio recording of you (voice notes) & 69.59 & 0.91 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/recordedyoutalkingtoyourself(makingvoicenotes)combined} \\ 
36 & medication taken & 69.49 & 1.01 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhatmedicationyoutakecombined} \\ 
37 & videos already on device & 68.89 & 0.88 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/sharedvideosyoutookwhicharealreadyonyourdevicecombined} \\ 
38 & photo of your signature & 68.07 & 0.84 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookapictureofyoursignaturecombined} \\ 
39 & web history & 66.44 & 1.01 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhatwebsitesyougotocombined} \\ 
40 & photos taken on device & 66.21 & 1.02 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/sharedphotosyoutookwhicharealreadyonyourdevicecombined} \\ 
41 & home address & 65.0 & 0.97 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhereyoulivesomehowcombined} \\ 
42 & fine-grained location tracking (+/- cm) & 63.51 & 0.99 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/trackedwhereyouareveryaccurately(whereyouareinaroom)combined} \\ 
43 & photo of people at random & 61.94 & 1.06 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookphotosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
44 & video downloaded from the internet & 61.49 & 1.00 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/sharedvideosyoudownloadedontheinternetsavedonyourdevicecombined} \\ 
45 & when you are alone & 61.27 & 0.99 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhenandhowmuchyouspendtimealonecombined} \\ 
46 & location tracking (+/- m) & 61.24 & 1.08 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/trackedwhereyouare(likeaGPS)combined} \\ 
47 & videos of people at random & 61.04 & 0.95 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookvideosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
48 & where you are currently going & 60.87 & 0.97 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhereyouarecurrentlygoingcombined} \\ 
49 & recording of sound around you & 60.45 & 0.94 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/recordedthesoundaroundyoucombined} \\ 
50 & people you spend time with & 60.0 & 1.13 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhoyouwerespendingtimewithcombined} \\ 
51 & workplace address & 58.09 & 1.16 &\includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhereyouworksomehowcombined} \\ 
52 & sounds on device (notifications, etc) & 54.4 & 1.29 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/copiedanduploadedsoundssavedonyourdevice(notificationnoisesetc)combined} \\ 
53 & phone usage & 51.95 &1.22 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedhowmuchyouuseyourphonecombined} \\ 
54 & purchased products & 50.0 & 1.09 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhatproductsyoubuycombined} \\ 
55 & when you are sick or healthy & 48.17  & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhenyouaresickorhealthycombined} \\ 
56 & how close you are to interacting people & 46.98 & 1.12 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedhowcloseyouaretootherpeopleyouinteractwithcombined} \\ 
57 & feelings (based on biometrics) & 46.81 & 1.31 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedhowyouwerefeelingbasedonheartratebreathingandortemperaturecombined} \\ 
58 & computer usage & 44.93 & 1.16 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedhowmuchyouuseyourcomputercombined} \\ 
59 & eating patterns & 42.86 & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhenhowmuchandwhatyouareeatingcombined} \\ 
60 & name & 42.54 & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedyournamecombined} \\ 
61 & sleeping patterns & 40.56 & 1.34 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhenandhowwellyouaresleepingcombined} \\ 
62 & eye patterns (for eye tracking) & 40.51 & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/scannedyoureyetolearnyoureyepatterns(foreyetracking)combined} \\ 
63 & exercise patterns & 38.66 & 1.26 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhenhowandhowmuchyouexercisecombined} \\ 
64 & when you are happy or having fun & 34.75 & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhenyouwerehappyorhavingfuncombined} \\ 
65 & television shows watched & 30.2 & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhattelevisionshowsyouwatchcombined} \\ 
66 & when you are busy or interruptible & 29.5 & 1.26 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhenyouarebusyorinterruptiblecombined} \\ 
67 & music on device & 28.06 & 1.43 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/copiedanduploadedmusicfromyourdevicecombined} \\ 
68 & heart rate & 27.5 & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedyourheartratecombined} \\ 
69 & age & 24.29 & 1.43 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedyouragecombined} \\ 
70 & language spoken & 15.86 & 1.49 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedthelanguageyouwerespeakingcombined} \\ 
71 & gender & 15.0 & 1.46 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedyourgendercombined} \\ 
